Figures and Tables

### 2021-01-15 paper/figures_tables.Rmd
adding figure

---
title: "Figures and Tables"
subtitle: " "
output:
  html_document:
      toc: true
bibliography: "../paper/mybibfile.bib"
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE, results = 'hide')
```

@@

```{r fig.width=2.5, fig.height=4}
plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "auto", label_size = 10)
#ggsave("testfig.tiff", dpi = 300, width = 3, units = "in")
```

@@

## Figure 4. 
Seed dispersal kernels produced by the three models considered with Weibull distribution overlaid

```{r fig.width=3}
bind_rows(null_dispersal %>% mutate(model = "Null"), 
          indiv_dispersal %>% mutate(model = "Individual"),
          fam_dispersal %>% mutate(model = "Family")) %>% 
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> dispersal_data

@@

```{r}
null_dispersal %>% 
  ggplot(., aes(x = dispersal)) +
  geom_histogram(aes(y = ..density..), binwidth = 50) +
  stat_function(fun = dweibull, n = 100, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2]),
                linetype = "solid", size = 1) +
  theme_bw() +
  labs(y = "Density", "Seed dispersal (m)") +
  lims(y = c(0, 0.004), x = c(0, 1500))
```

@@

all_disp_data %>% 
  ggplot(., aes(y = mean_dispersal, group = model)) +
  #facet_wrap(~model, ncol = 3) +
  geom_boxplot() +
  theme_bw()  +
  labs(y = "Seed dispersal (m)") -> b

all_disp_data %>% 
  ggplot(., aes(y = seed_dispersion)) +
  facet_wrap(~model, ncol = 3) +
  geom_boxplot() +
  theme_bw() +
  theme(strip.background = element_blank(),
        strip.text = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "Dispersion (m)") -> c

#plot_grid(a,b, nrow = 2)

@@

>>>>

---
title: "Figures and Tables"
subtitle: ' '
output:
  html_document:
    toc: yes
  word_document:
    toc: yes
bibliography: ../paper/mybibfile.bib
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

@@

```{r fig.width=2.5, fig.height=4}
plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "auto", label_size = 10)
```

@@

```{r eval = FALSE,  fig.width=3}
bind_rows(null_dispersal %>% mutate(model = "Null"), 
          indiv_dispersal %>% mutate(model = "Individual"),
          fam_dispersal %>% mutate(model = "Family")) %>% 
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> dispersal_data

@@

```{r eval = FALSE}
null_prms <- null_weibull$estimate
null_sd <- null_weibull$sd
null_dispersal %>% 
  ggplot(., aes(x = dispersal)) +
  geom_histogram(aes(y = ..density..), color = "grey", fill = "grey") +
  stat_function(fun = dweibull, n = 100, args = list(shape = null_prms[1], scale = null_prms[2]),
                linetype = "solid", size = 1, color = "black") +
  theme_bw() +
  labs(y = "Density", x = "Seed dispersal (m)") +
  lims(y = c(0, 0.004), x = c(0, 1500)) -> null_kernel

indiv_prms <- indiv_weibull$estimate
indiv_sd <- indiv_weibull$sd
indiv_dispersal %>% 
  ggplot(., aes(x = dispersal)) +
  geom_histogram(aes(y = ..density..), color = "grey", fill = "grey") +
  stat_function(fun = dweibull, n = 100, args = list(shape = indiv_prms[1], scale = indiv_prms[2]),
                linetype = "solid", size = 1, color = "black") +
  theme_bw() +
  labs(y = "Density", x = "Seed dispersal (m)") +
  lims(y = c(0, 0.004), x = c(0, 1500)) -> indiv_kernel

fam_prms <- fam_weibull$estimate
fam_sd <- fam_weibull$sd
fam_dispersal %>% 
  ggplot(., aes(x = dispersal)) +
  geom_histogram(aes(y = ..density..), color = "grey", fill = "grey") +
  stat_function(fun = dweibull, n = 100, args = list(shape = fam_prms[1], scale = fam_prms[2]),
                linetype = "solid", size = 1, color = "black") +
  theme_bw() +
  labs(y = "Density", x = "Seed dispersal (m)") +
  lims(y = c(0, 0.004), x = c(0, 1500)) -> fam_kernel

plot_grid(null_kernel, indiv_kernel, fam_kernel, ncol = 1)
```

## Figure 4. 
Box plots to show the distribution of mean seed dispersal distance and seed dispersion per simulation run. In this case, we are looking at the data per simulation run, since we calculate seed dispersion in relation to the mean seed location, and this is done for each simulation run with five seeds each. Here, we consider mean seed dispersal as the distance from the origin to the mean seed location for each simulation run.

@@

all_disp_data %>% 
  ggplot(., aes(y = mean_xy_dispersal, x = model)) +
  geom_boxplot() +
  theme_bw() +
  labs(y = "Mean dispersal (m)") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank()) -> a

all_disp_data %>% 
  ggplot(., aes(y = seed_dispersion, x = model)) +
  geom_boxplot() +
  theme_bw() +
  labs(y = "Seed dispersion (m)") +
  theme(axis.title.x = element_blank()) -> b

plot_grid(a,b, nrow = 2)

@@

# Table 1.

```{r}
dispersal_kernel_table <- data.frame(
  Model = c("Null", "Individual", "Family"),
  Mean_dispersal = c(signif(mean(null_dispersal$dispersal), 4),
                     signif(mean(indiv_dispersal$dispersal), 4),
                     signif(mean(fam_dispersal$dispersal),4)),
  Seed_dispersion = c(signif(mean(null_dispersion$seed_dispersion), 4),
                      signif(mean(indiv_dispersion$seed_dispersion), 4),
                      signif(mean(fam_dispersion$seed_dispersion),4)),
  Max_dispersal = c(signif(max(null_ldd$global_max), 4),
                           signif(max(indiv_ldd$global_max), 4),
                           signif(max(fam_ldd$global_max), 4)),
  # Max_dispersal = c(paste0(signif(null_ldd$max_mean, 3), " (", signif(null_ldd$max_sd, 1), ")"),
  #                   paste0(signif(indiv_ldd$max_mean, 3), " (", signif(indiv_ldd$max_sd, 1), ")"),
  #                   paste0(signif(fam_ldd$max_mean, 3), " (", signif(fam_ldd$max_sd, 1), ")")),
  LDD = c(paste0(signif(null_ldd$prcnt_ldd, 3), " (", signif(null_ldd$sd_ldd, 1), ")", "%"),
          paste0(signif(indiv_ldd$prcnt_ldd, 3), " (", signif(indiv_ldd$sd_ldd, 1), ")", "%"),
          paste0(signif(fam_ldd$prcnt_ldd, 3), " (", signif(fam_ldd$sd_ldd, 1), ")", "%")),
  Weibull_Shape = c(paste0(signif(null_weibull$estimate[1], 4), " (", signif(null_weibull$sd[1], 2), ")"),
                    paste0(signif(indiv_weibull$estimate[1], 4), " (", signif(indiv_weibull$sd[1], 2), ")"),
                    paste0(signif(fam_weibull$estimate[1], 4), " (", signif(fam_weibull$sd[1], 2), ")")),
  Weibull_Scale = c(paste0(signif(null_weibull$estimate[2], 4), " (", signif(null_weibull$sd[2], 2), ")"),
                     paste0(signif(indiv_weibull$estimate[2], 4), " (", signif(indiv_weibull$sd[2], 2), ")"),
                     paste0(signif(fam_weibull$estimate[2], 4), " (", signif(fam_weibull$sd[2], 2), ")"))

)
